% CVS info
\RCS$Revision: 1.7 $
\RCS$Date: 2008/10/28 20:02:21 $
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------------------------
%%% put your own definitions here:
 
%%%%%%%%%%%%%%%%
% Declarations %
%%%%%%%%%%%%%%%%
%\def\bb{$\mathrm{b}\overline{\mathrm{b}}\;$}
%\def\cc{$\mathrm{c}\overline{\mathrm{c}}\;$}
\def\bb{$b\overline{b}\;$}
\def\cc{$c\overline{c}\;$}
\def\ttbar{$t\overline{t}\;$}
\def\mttbar{$m_{t\overline{t}}\;$}
\def\Zp{${Z'}\;$}
\def\ddZ{$\mathrm{d}\overline{\mathrm{d}}$}
\def\ss{$\mathrm{s}\overline{\mathrm{s}}\;$}
%\def\ttbar{$\mathrm{t}\overline{\mathrm{t}}\;$}
\def\ssZ{$\mathrm{s}\overline{\mathrm{s}}$}
\def\zqq{$\mathrm{Z} \rightarrow \mathrm{q}\overline{\mathrm{q}}\;$}
\def\zcc{$\mathrm{Z} \rightarrow \mathrm{c}\overline{\mathrm{c}}\;$}
\def\zbb{$\mathrm{Z} \rightarrow \mathrm{b}\overline{\mathrm{b}}\;$}
\def\zuuZ{$\mathrm{Z} \rightarrow \mathrm{u}\overline{\mathrm{u}}$}
%\def\gev{~GeV/$c\;$}
\def\gevc{~GeV/$c\;$}
\def\gevcc{~GeV/$c^{2}\;$}
\def\mum{~$\mu$m$\;$}
\def\pt{$p_T\;$}
\def\ptZ{$p_T$}
\def\Et{$E_T\;$}
\def\EtZ{$E_T$}
\def\ip{$IP\;$}
\def\ipZ{$IP$}
\def\dca{$dca\;$}
\def\prob{${\cal P}_{jet}\;$}
\def\probZ{${\cal P}_{jet}$}
\def\dr{$\Delta R\;$}
\def\pscat{$p_{scat}\;$}
\def\pscatZ{$p_{scat}$}
\def\sip{${\cal S}_{IP}\;$}
%\def\ptrel{$p_T^{\rm rel}}
\def\ptrel{$p_{Trel}\;$}
%\def\ptrelZ{$p_{Trel}$}
\def\tag{${\cal P}_{jet}^+<$}
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
% select one of the following and type in the proper number:
\cmsNoteHeader{2008/081}

\title{\bf Measurement of the $b$ tagging Performance using a Muon in Jets Sample: Update of the System8 Method with the CSA07 MC samples.}

%\author[iphc]{J\'er\'emy Andrea, Daniel Bloch, Denis Gel\'e, Pierre Juillot}
%\author[uic]{V\'ictor E. Bazterra, Cecilia E. Gerber}
%\author[brown] {Meenakshi Narain}
\author[purdue]{Pratima Jindal}
\author[fnal]{Francisco Yumiceva}
%\address[uic]{University of Illinois at Chicago, Chicago, IL 60607, USA}
%\address[iphc]{Institut Pluridisciplinaire Hubert Curien, Universit\'e Louis Pasteur, CNRS/IN2P3, Strasbourg, France}
%\address[brown]{Brown University, Providence, RI 02912, USA}
\address[fnal]{Fermi National Accelerator Laboratory, Batavia, Illinois USA}  
\address[purdue]{Purdue University Calumet, Hammond, Indiana, USA}
\date{\today}
  
\abstract{
This note describes the improvements developed since the analysis note CMS AN 2007/046 using the CSA07 MC samples. The System8 method has been 
extended to consider correlations for the soft muon tagger. In this 
case the soft muon tagger is a simple tagger based only in the 
$p_{Trel}$ distribution. We also study the System8 convergence 
and developed options to choose the best solution in case multiple 
solutions are available. As a results, the convergence range 
in jet $p_T$ of this
method has been extended compared to the previous analysis.
}

% these need to be filled in by hand
\hypersetup{%
pdfauthor={Francisco Yumiceva},%
pdftitle={CMS Note 2008/0XX},%
pdfsubject={CMS},%
pdfkeywords={CMS, physics, btagging, muon,b}}


\maketitle %maketitle comes after all the front information has been supplied

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Begin text %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
%DB
\setcounter{page}{2}
%DB
 
\input{Introduction}
\label{sec:intro}

\input{Samples}
%\label{sec:samples}
\input{TaggingAlgos}
\label{sec:taggingalgos}

\input{Distributions}
\label{sec:distributions}

\clearpage
\input{System8}
\label{sec:system8}

\input{SLTefficiency}
\clearpage
\input{Average_results}
\label{sec:avg_results}
\clearpage
\input{BinnedResults}
\label{sec:binned_results}

\input{Conclusions}
\label{sec:conclusions}

\section{Acknowledgment} 
We would like to thank Daniel Bloch and J\'er\'emy Andrea for their comments and for providing
us with the tools to solve System8. Meenakshi Narain for her advise on this analysis. Last but not
least we would like to thank Cecilia Gerber for her detail comments on the note and her
advise.

\appendix
\input{ExtraDistributions}
%DB \label{sec:correlations}

\begin{thebibliography}{99}

\bibitem{ref:btag_oldnote}
M.~Narain, P.~Tan, F.~Yumiceva, J~.Andrea, D.~Bloch, D.~Gel\'e, P.~Juillot
V.~Bazterra, C.~Gerber, ``Performance Measurement of $b$ tagging Algorithms Using Data containing Muons within Jets'', 
{\bf CMS AN-2007/046 (2007)}.

\bibitem{ref:csa07}
https://twiki.cern.ch/twiki/bin/view/Main/AlpgenSummer07.

\bibitem{ref:pythia}
T.~Sj{\"o}strand, L.~Lonnblad and S.~Mrenna, 
{\bf hep-ph/0108264} (2001).

\bibitem{ref:alpgen}
M.~L.~Mangano, M.~Moretti, F.~Piccinini, R.~Pittau, and A.~D.~Polosa, ``ALPGEN, a generator for hard multiparton processes in hadronic collisions''. 
{\bf JHEP 07 (2003) 001, arXiv:hep-ph/0206293}.

\bibitem{ref:iterativecone5}
P.~Schieferdecker et al., ``Performance of Jet Algorithms in CMS''. 
{\bf CMS Analysis Note 2008/001 (2008)}.

\bibitem{ref:cmsip} 
    A.~Rizzi, F.~Palla, G.~Segneri,
    {\em Track impact parameter based b-tagging with CMS}, 
    {\bf CMS Note 2006/019}. 
 
\bibitem{ref:root}
ROOT analysis system 
http://root.cern.ch/

\end{thebibliography}
 
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
