\section{Introduction}

The measurement of the $b$-tagging performance using a sample of muon-in-jets is described
in the CMS Analysis Note~\cite{ref:btag_oldnote}. Three methods were
studied in detail in Ref.~\cite{ref:btag_oldnote}: System8, $p_{Trel}$,
and counting. The methods parametrize the $b$-tagging efficiency and mistagging rate 
as a function of jet $p_T$ or jet $\eta$. These efficiencies can be applied to analyses which
rely on $b$-tagging and Monte Carlo studies (MC).

In this note, the System8 will be described in more detail. This method is based in the use of two weakly correlated
$b$-taggers and two sets of a muon-in-jet sample. One sample is a subset of the
muon-in-jet sample where an away-jet is tagged as a $b$-jet. The correlations
between the two $b$-taggers and between the two samples are estimated
from Monte Carlo. The flavor contributions are written for 
each combination of sample and tagger producing a system of eight
equations. The results of the system-of-equation are the
$b$-tagging efficiencies and charm+light quark and gluon mistagging 
for the two tagger applied on the samples. 

This note also describes the improvements developed since the analysis in Ref.~\cite{ref:btag_oldnote}. The System8 method has been extended to consider correlations for the soft
muon tagger. In this case the soft muon tagger is a simple tagger based only in the $p_{Trel}$
distribution. We also study the System8 convergency and developed options to choose the best
solution in case of multiple solutions. As a results, the convergency range in jet $p_T$ of this
method has been extended compared to the previous analysis~\cite{ref:btag_oldnote}. The analysis was done using the CMSSW 1.6.X release and the
CSA07 MC samples~\cite[ref:csa07].
 
